Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Livre
Update Livre description and volume reference.

git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@55 db7c848b-7755-4df2-b763-8796797afa52

{\em Equalizers} are an addition to compound trees. They modify parameters of
their respective subtree at runtime to dynamically optimize the resource usage,
by each tuning one aspect of the decomposition. Due to their nature, they are
transparent to application developers, but might have application-accessible
parameters to tune their behavior. Resource equalization is the critical
component for scalable parallel rendering, and therefore the eponym for the
\textsf{Equalizer} project name. \FIXME{ok, this is a bit tricky to have Equalizer as a
name for the framework as well as for this component, can't we change this?
eile: We can't change the product name, and changing the component name will be
hard. In fact, this is an artefact of the sw architecture: The runtime balancing
of resources is the core contribution of Equalizer, and therefore the equalizers
performing this task are the name-givers for the product. Modified paragraph
above for clarity.}

@@

Livre (Large-scale Interactive Volume Rendering Engine) is an out-of-core
parallel 4D volume renderer. It supports sort-first decomposition, both for
scalability as well as for driving large-scale tiled display walls. The
out-of-core loading of data relies on a shared file system, only the high-level
state, e.g., camera position and rendering settings, are shared through \textsf{Collage}
objects.

>>>>

{\em Equalizers} are an addition to compound trees. They modify parameters of
their respective subtree at runtime to dynamically optimize the resource usage,
by each tuning one aspect of the decomposition. Due to their nature, they are
transparent to application developers, but might have application-accessible
parameters to tune their behavior. Resource equalization is the critical
component for scalable parallel rendering, and therefore the eponym for the
\textsf{Equalizer} project name. \FIXME{modified paragraph is ok; we
have to ensure that the font differs between the Equalizer project and the
Equalizer components consistently throughout the text}

@@

Livre (Large-scale Interactive Volume Rendering Engine) is a GPU ray-casting based parallel
4D volume renderer, implementing state-of-the-art view-dependent level-of-detail rendering (LOD)
and out-of-core data management~\cite{EHKRW:06}. Hierarchical and out-of-core LOD
data management is supported by an implicit volume octree, accessed asynchronously
by the renderer from a data source on a shared file system. Different data sources providing
an octree conform access to RAW or compressed as well as to implicitly generated volume data
(e.g. such as from event simulations or surface meshes) can be used.

High-level state information, e.g., camera position and rendering settings, is shared in Livre
through \textsf{Collage} objects between the parallel applications and rendering threads.
Sort-first decomposition is efficiently supported through octree traversal and culling both
for scalability as well as for driving large-scale tiled display walls.
